Data Sources

### 2021-05-19 notebook/model-estimates.Rmd
...

scale <- 20
x <- siteA$PopulationUntransformed / scale
constants <- list(N = length(siteA$SampleYear),
                  x0 = x[[1]]
)
```

```{r}
logistic  <- nimble::nimbleCode({
  r ~ dunif(0,2)
  K ~ dunif(0,10)
  sigma ~ dunif(0,.4)
  x[1] <- x0
  for(t in 1:(N-1)){
    mu[t] <- x[t] + x[t] * r * (1 - x[t] / K)
    x[t+1] ~ dlnorm(log(mu[t]), sd = sigma)
  }

@@

```{r}
may  <- nimble::nimbleCode({
  x[1] <- x0
  q <- 3
  s <- 2
  r ~ dlnorm(log(.7) - s^2/2, s)
  K ~ dlnorm(log(1.2)- s^2/2, s)
  a ~ dlnorm(log(0.2) - s^2/2,  s)
  b ~ dlnorm(log(0.15) - s^2/2, s)
  sigma ~ dlnorm(log(0.05) - s^2/2, s)

@@

```{r}
l_draws <- mcmc(logistic, x, constants)
l_draws %>% summarise(across(everything(), list(mean = mean, sd = sd)))

```
```{r}
bayesplot::mcmc_trace(l_draws)
```

```{r}
m_draws <- mcmc(may, x, constants)
m_draws %>% summarise(across(everything(), list(mean = mean, sd = sd)))
bayesplot::mcmc_trace(m_draws)

@@

>>>>

#scale <- 20
x <- siteA$PopulationUntransformed / scale
constants <- list(N = length(siteA$SampleYear),
                  x0 = x[[1]]
)
```

```{r}
logistic  <- nimble::nimbleCode({
  r ~ dunif(0,5)
  K ~ dunif(0,30)
  sigma ~ dunif(0,.4)
  x[1] <- x0
  for(t in 1:(N-1)){
    mu[t] <- x[t] + x[t] * r * (1 - x[t] / K)
    x[t+1] ~ dlnorm(log(mu[t]), sd = sigma)
  }

@@

```{r}
#p <- list(r = 2, K = 25, q = 4, b = 2, a = 7) # higher-state peak is optimal

may  <- nimble::nimbleCode({
  x[1] <- x0
  q <- 3
  s <- 2
  r ~ dunif(0,5) #dlnorm(log(1) - s^2/2, s)
  K ~ dunif(0,40) #dlnorm(log(2)- s^2/2, s)
  a ~ dunif(0,5) # dlnorm(log(7) - s^2/2,  s)
  b ~ dunif(1.5,2.5) #dlnorm(log(1) - s^2/2, s)
  sigma ~ dlnorm(log(0.05) - s^2/2, s)

@@

```{r}
l_draws <- mcmc(logistic, x, constants)
l_p <- l_draws %>% summarise(across(everything(), list(mean = mean, sd = sd)))
bayesplot::mcmc_trace(l_draws)
```

```{r}
m_draws <- mcmc(may, x, constants)
p <- m_draws %>% summarise(across(everything(), list(mean = mean, sd = sd)))
bayesplot::mcmc_trace(m_draws)

@@

```{r}

may_f <- function(x){ # May
      x + x * p$r_mean * (1 - x / p$K_mean)  - (p$a_mean) * x ^ 3 / (x ^ 3 + (p$b_mean) ^ 3)
}

# Matches the optimal policy under these settings (depends on sigma, among others)
logistic_f <- 
  function(x){
      x + x * l_p$r_mean * (1 - x / l_p$K_mean)
  }

states <- seq(0,30, length=200)
landscape <- map_dfr(list(may_f, logistic_f), 
                     function(f) tibble(state = states, f = f(states) -states),
                     .id = "model")

landscape %>% ggplot(aes(state, f, col=model)) + geom_point()
```

### 2021-05-19 notebook/tipping-decisions.Rmd
...

```{r}
states <- seq(0,2, length=100)
actions <- seq(0,2, length.out = 100)
observations <- states
sigma_g <- 0.05
sigma_m <- 0.0

@@

@@

# Matches the optimal policy under these settings (depends on sigma, among others)
logistic_1 <- 
  function(x, h = 0){
    y <- x +  h
    r <- p$r - 0.09

@@

```{r}
nothing <- rep(1, length(states))
m <- matrices[[3]]
x0 = which.min(abs(states - 0.7))
sim <- mdp_planning(m$transition, m$reward, discount, model_prior = c(1), 
                   policy = nothing, x0 = x0, Tmax = 1000)
sim %>% mutate(state = states[state], action = actions[action]) %>% 
  ggplot(aes(time, state)) + geom_point()+geom_path() + 
  geom_point(aes(time, action), col="blue")

>>>>

```{r}
states <- seq(0,30, length=100)
actions <- seq(0,30, length.out = 100)
observations <- states
sigma_g <- 0.05
sigma_m <- 0.0

@@

#p <- list(r =.7, K = 1.2, q = 3, b = 0.15, a = 0.2) # lower-state peak is optimal
p <- list(r = 2, K = 25, q = 4, b = 2, a = 7) # higher-state peak is optimal

@@

# Matches the optimal policy under these settings (depends on sigma, among others)
logistic_1 <- 
  function(x, h = 0){
    y <- x +  h
    r <- p$r - 0.2

@@

```{r}
nothing <- rep(1, length(states))
m <- matrices[[3]]
x0 = which.min(abs(states - 17))
sim <- mdp_planning(m$transition, m$reward, discount, model_prior = c(1), 
                   policy = nothing, x0 = x0, Tmax = 1000)
sim %>% mutate(state = states[state], action = actions[action]) %>% 
  ggplot(aes(time, state)) + geom_point()+geom_path() + 
  geom_point(aes(time, action), col="blue")
